Juliacon Proceedings in Quarto

### 2023-11-14 template.qmd

---
title: Juliacon Proceedings in Quarto
format:
  juliacon-proceedings-pdf:
    keep-tex: true  
  juliacon-proceedings-html: default
author:
  - name: Patrick Altmeyer
    affiliations:
      - Delft University of Technology
    orcid: 0000-0003-4726-8613
    email: p.altmeyer@tudelft.nl
    url: https://www.paltmeyer.com/
  - name: Cynthia C. S. Liem
    affiliations:
      - Delft University of Technology
abstract: |
  This document is a Quarto template demonstrating the `juliacon-proceedings` format.
year: 2022
keywords: [Template, Demo, Quarto, JuliaCon]
bibliography: bibliography.bib  
---

@@

*TODO* Create a template that demonstrates the appearance, formatting, layout, and functionality of your format. Learn more about journal formats at <https://quarto.org/docs/journals/>.

## Proof-of-Concept

This is a proof-of-concept for how we could use Quarto for JuliaCon proceedings. For current submissions, please ignore this repo and follow the official instructions [here](https://github.com/JuliaCon/JuliaConSubmission.jl).

## Executable Code

@@

## Code Listings

>>>>

---
title: Juliacon Proceedings in Quarto
format:
  juliacon-proceedings-pdf:
    keep-tex: true  
  juliacon-proceedings-html: default
author:
  - name: Patrick Altmeyer
    affiliations:
      - Delft University of Technology
    orcid: 0000-0003-4726-8613
    email: p.altmeyer@tudelft.nl
    url: https://www.paltmeyer.com/
abstract: |
  This document is a Quarto template demonstrating the `juliacon-proceedings` format.
year: 2023
keywords: [Template, Demo, Quarto, JuliaCon]
bibliography: bibliography.bib  
---

@@

This is a template for writing a JuliaCon Proceedings article in Quarto. This is a proof-of-concept for how we could use Quarto for JuliaCon proceedings. For current submissions, please ignore this repo and follow the official instructions [here](https://github.com/JuliaCon/JuliaConSubmission.jl).

## What is Quarto?

[Quarto](https://quarto.org/) makes it easy to write reproducible documents that can be rendered to PDF, HTML, Word and more. It is based on Markdown, which is easy to learn and write. It also supports LaTeX, which is useful for more advanced formatting. As this extension demonstrates, Quarto is also very flexible and can be extended with custom templates and styles.

## Why Quarto?

By embracing Quarto, JuliaCon Proceedings can set an example for how to write reproducible documents. We would not only make it easier for authors to write their submissions but also open the door for more advanced features such as interactive figures and executable code blocks in HTML documents.

## About this template

This template is based on the existing [JuliaCon Proceedings LaTeX template](https://github.com/JuliaCon/JuliaConSubmission.jl).

## How to use this template

> The remainder of this document repeats relevant elements from the [JuliaCon Proceedings LaTeX template].

# The JuliaCon Article Class {#sec-documentclass}

The `juliacon` class file preserves the standard LATEX{} interface such that any document that can be produced using the standard LATEX{} article class can also be produced with the class file.

It is likely that the make up will change after file submission. For this reason, we ask you to ignore details such as slightly long lines, page stretching, or figures falling out of synchronization, as these details can be dealt with at a later stage.

Use should be made of symbolic references (\verb|\ref| ) in order to protect against late changes of order, etc.

# Executable Code

@@

# Code Listings

### 2023-11-14 template.tex

\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Juliacon Proceedings in Quarto},
  pdfauthor={Patrick Altmeyer; Cynthia C. S. Liem},
  pdfkeywords={Template, Demo, Quarto, JuliaCon},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\author[1]{Patrick Altmeyer}
\author[1]{Cynthia C. S. Liem}
\affil[1]{Delft University of Technology}
\date{}
\begin{document}
\maketitle

@@

% Hypersetup
\hypersetup{
    pdftitle = {Juliacon Proceedings in Quarto},
    pdfsubject = {JuliaCon 2022 Proceedings},
    pdfauthor = {Patrick Altmeyer, Cynthia C. S. Liem},
    pdfkeywords = {Template, Demo, Quarto, JuliaCon},
}

@@

\emph{TODO} Create a template that demonstrates the appearance,
formatting, layout, and functionality of your format. Learn more about
journal formats at \url{https://quarto.org/docs/journals/}.

\subsection{Proof-of-Concept}\label{proof-of-concept}

This is a proof-of-concept for how we could use Quarto for JuliaCon
proceedings. For current submissions, please ignore this repo and follow
the official instructions
\href{https://github.com/JuliaCon/JuliaConSubmission.jl}{here}.

\subsection{Executable Code}\label{executable-code}

@@

\subsection{Code Listings}\label{code-listings}

>>>>

\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Juliacon Proceedings in Quarto},
  pdfauthor={Patrick Altmeyer},
  pdfkeywords={Template, Demo, Quarto, JuliaCon},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\author[1]{Patrick Altmeyer}
\affil[1]{Delft University of Technology}
\date{}
\begin{document}
\maketitle

@@

% Hypersetup
\hypersetup{
    pdftitle = {Juliacon Proceedings in Quarto},
    pdfsubject = {JuliaCon 2023 Proceedings},
    pdfauthor = {Patrick Altmeyer},
    pdfkeywords = {Template, Demo, Quarto, JuliaCon},
}

@@

This is a template for writing a JuliaCon Proceedings article in Quarto.
This is a proof-of-concept for how we could use Quarto for JuliaCon
proceedings. For current submissions, please ignore this repo and follow
the official instructions
\href{https://github.com/JuliaCon/JuliaConSubmission.jl}{here}.

\subsection{What is Quarto?}\label{what-is-quarto}

\href{https://quarto.org/}{Quarto} makes it easy to write reproducible
documents that can be rendered to PDF, HTML, Word and more. It is based
on Markdown, which is easy to learn and write. It also supports LaTeX,
which is useful for more advanced formatting. As this extension
demonstrates, Quarto is also very flexible and can be extended with
custom templates and styles.

\subsection{Why Quarto?}\label{why-quarto}

By embracing Quarto, JuliaCon Proceedings can set an example for how to
write reproducible documents. We would not only make it easier for
authors to write their submissions but also open the door for more
advanced features such as interactive figures and executable code blocks
in HTML documents.

\subsection{About this template}\label{about-this-template}

This template is based on the existing
\href{https://github.com/JuliaCon/JuliaConSubmission.jl}{JuliaCon
Proceedings LaTeX template}.

\subsection{How to use this template}\label{how-to-use-this-template}

\begin{quote}
The remainder of this document repeats relevant elements from the
{[}JuliaCon Proceedings LaTeX template{]}.
\end{quote}

\section{The JuliaCon Article Class}\label{sec-documentclass}

The \texttt{juliacon} class file preserves the standard LATEX\{\}
interface such that any document that can be produced using the standard
LATEX\{\} article class can also be produced with the class file.

It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.

Use should be made of symbolic references (\verb|\ref| ) in order to
protect against late changes of order, etc.

\section{Executable Code}\label{executable-code}

@@

\section{Code Listings}\label{code-listings}
